FAIR fission track analysis with geochron@home

### 2025-07-30 geochron@home/manuscript/paper.tex
Removed logcontrasts

The context here is rather different from that in
Figure~\ref{fig:AvP}b, where we were comparing the ratios of counts
made by two analysts on each of 25 grains. Here we are comparing the
ratios of counts for the same two grains made by each of 37
analysts. There is no theoretical justification for
Equation~\ref{eq:N12} here, but it still provides a useful benchmark
for assessing variation between the ratios. In
Figure~\ref{fig:radialcrowd}c, that variation is consistent with
Poisson variation (as it is for most other pairs of grains) but with
expert counters one would expect less variation than that. However, in
spite of the under-counting by the students, the pooled students'
ratio of 0.97 is close to PV's ratio of 1.04. This happens quite often
in this data set, but not always, and there are some pairs of grains
where the students' pooled ratio differs somewhat from PV's.  The
logcontrast between the student ratios and PV's ratios for all 300
pairs of grains follows a normal distribution with a mean of 0.0 and
standard deviation 0.23 (Table~\ref{tab:logcontrasts}). This indicates
that, on the whole, the student estimates of the (log)ratios are
unbiassed with respect to the expert opinion of PV.
\medskip

@@

\clearpage

\begingroup
\captionof{table}{
  Logcontrasts between the pooled count ratio of the
  students and PV for each pair of 25 grains in
  Table~\ref{tab:crowdtable}.
}
\label{tab:logcontrasts}\medskip
\renewcommand{\arraystretch}{0.7}
\begin{scriptsize}
  \input{../output/logcontrasts.txt}
\end{scriptsize}
\endgroup

>>>>

The context here is rather different from that in
Figure~\ref{fig:AvP}b, where we were comparing the ratios of counts
made by two analysts on each of 25 grains. Here we are comparing the
ratios of counts for the same two grains made by each of 37
analysts. There is no theoretical justification for
Equation~\ref{eq:N12} here, but it still provides a useful benchmark
for assessing variation between the ratios. In
Figure~\ref{fig:radialcrowd}c, that variation is consistent with
Poisson variation (as it is for most other pairs of grains) but with
expert counters one would expect less variation than that. However, in
spite of the under-counting by the students, the pooled students'
ratio of 0.97 is close to PV's ratio of 1.04. This happens quite often
in this data set, but not always, and there are some pairs of grains
where the students' pooled ratio differs somewhat from PV's.
\medskip

@@
